Mixture Models for Single-Cell Assays with Application to Vaccine Studies

### 2013-05-15 MIMOSA.tex
Updated figure 1
Update legend for Figure 2

\documentclass[12pt,oupdraft]{biostatistics}
%\usepackage{tikz}
%\usetikzlibrary{calc}
%\usetikzlibrary{positioning}
%\usepackage{authblk}
\usepackage{amsmath}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig1.eps}
%\begin{tikzpicture} [auto, node distance=0cm]
%\node at (0,0) (A){
%    \begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (foo) {\includegraphics[width=0.95\columnwidth]{Figures/2.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%    \node at (0,1) [font=\small\sffamily] {A} ;
%    \node at (0.5,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%\end{tikzpicture}
% };
% \node [below=of A] (B) {
% \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (bar){\includegraphics[width=0.95\columnwidth]{Figures/1.pdf}};
%    \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \node at (0.5,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
% };
%  \node [below=of B] (E) {
% \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (baz){\includegraphics[width=0.95\columnwidth]{Figures/15.pdf}};
%    \begin{scope} [x={(baz.south east)},y={(baz.north west)}]
%    \node at (0,1) [font=\small\sffamily] {E} ;
%    \node at (0.5,1) [font=\small\sffamily] {F} ;
%    \end{scope}
%    \end{tikzpicture}
% };
%\end{tikzpicture}
   \caption{Performance of MIMOSA (EM and MCMC implementations, one-sided model) and competing methods on ICS data from the example flow cytometry data set. Sensitivity and specificity (ROC analysis) as well as observed and nominal false discovery rates for positivity calls from CD4+ T-cells stimulated with A-B) ENV-1-PTEG and expressing IFN-$\gamma$ or C-D) ENV-1-PTEG and expressing IL2. E-F) ENV-1-PTEG and expressing IFN-$\gamma$ and/or IL2. ROC and FDR plots of other cytokine combinations can be found in Supplementary Figure 1.This figure appears in color in the electronic version of this article.}
\label{fig:HVTN065}
\end{figure}

\begin{figure}
\centering
\includegraphics{TIKZFig2.eps}
%\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_plot1.pdf}};
%\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
%\node at (0,1) [font=\small\sffamily] {A} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [right=of A] (B) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_plot2.pdf}};
%\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%\node at (-0.1,1.1) [font=\small\sffamily] {B} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [below=of A] (C) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.45\columnwidth]{Figures/FluidigmFisher.pdf}};
%\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
%\node at (-0.05,1) [font=\small\sffamily] {C} ;
%\end{scope}
%\end{tikzpicture}
%};
%\end{tikzpicture}
\caption{Signed posterior probability, difference and log-odds ratio of the proportion of single-cells expressing each gene on a 96x96 Fluidigm array. The posterior probability of response times the sign of the change in expression is shown in A) (red indicates a decrease, green an increase, relative to the control). Columns and rows are clustered based on these signed posterior probabilities. B) The posterior differences in proportion of cells expressing a gene in the stimulated vs. control samples. Rows and columns are ordered as in A) for comparison. The traces show the deviations of each cell from zero. Colors along the columns denote different stimulations (green: CMV pp65 nlv5, red: HIV Gag, orange: HIV Nef, yellow: CMV pp65 tm10). C) Clustering of the signed q-values from Fisher's exact test. Genes selected from Fisher's exact test at the 10\% FDR level. This figure appears in color in the electronic version of this article.}
\label{fig:fluidigm}
\end{figure}

>>>>

\documentclass[12pt,oupdraft]{biostatistics}
\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
%\usepackage{authblk}
\usepackage{amsmath}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig1.eps}
%\begin{tikzpicture} [auto, node distance=0cm]
%\node at (0,0) (A){
%    \begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (foo) {\includegraphics[width=0.95\columnwidth]{Figures/revised_2.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%    \node at (0,1) [font=\small\sffamily] {A} ;
%    \node at (0.5,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%\end{tikzpicture}
% };
% \node [below=of A] (B) {
% \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (bar){\includegraphics[width=0.95\columnwidth]{Figures/revised_1.pdf}};
%    \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \node at (0.5,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
% };
%  \node [below=of B] (E) {
% \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (baz){\includegraphics[width=0.95\columnwidth]{Figures/revised_15.pdf}};
%    \begin{scope} [x={(baz.south east)},y={(baz.north west)}]
%    \node at (0,1) [font=\small\sffamily] {E} ;
%    \node at (0.5,1) [font=\small\sffamily] {F} ;
%    \end{scope}
%    \end{tikzpicture}
% };
%\end{tikzpicture}
   \caption{Performance of MIMOSA (EM and MCMC implementations, one-sided model) and competing methods on ICS data from the example flow cytometry data set. Sensitivity and specificity (ROC analysis) as well as observed and nominal false discovery rates for positivity calls from CD4+ T-cells stimulated with A-B) ENV-1-PTEG and expressing IFN-$\gamma$ or C-D) ENV-1-PTEG and expressing IL2. E-F) ENV-1-PTEG and expressing IFN-$\gamma$ and/or IL2. ROC and FDR plots of other cytokine combinations can be found in Supplementary Figure 1.This figure appears in color in the electronic version of this article.}
\label{fig:HVTN065}
\end{figure}

\begin{figure}
\centering
\includegraphics{TIKZFig2.eps}
%\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_plot1.pdf}};
%\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
%\node at (0,1) [font=\small\sffamily] {A} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [right=of A] (B) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Fluidigm_plot2.pdf}};
%\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
%\node at (-0.1,1.1) [font=\small\sffamily] {B} ;
%\end{scope}
%\end{tikzpicture}
%};
%\node [below=of A] (C) {
%\begin{tikzpicture}
%\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.45\columnwidth]{Figures/FluidigmFisher.pdf}};
%\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
%\node at (-0.05,1) [font=\small\sffamily] {C} ;
%\end{scope}
%\end{tikzpicture}
%};
%\end{tikzpicture}
\caption{Signed posterior probability and difference in empirical  in proportions of single-cells expressing each gene on a 96x96 Fluidigm array. The posterior probability of response times the sign of the change in expression is shown in A) (red indicates a decrease, green an increase, relative to the control) for a model fit to each stimulation and gene separately. Columns and rows are clustered based on these signed posterior probabilities. B) The empirical differences in proportion of cells expressing a gene in the stimulated vs. control samples. Rows and columns are ordered as in A) for comparison. The traces show the deviations of each cell from zero. Colors along the columns denote different stimulations (green: CMV pp65 nlv5, red: HIV Gag, orange: HIV Nef, yellow: CMV pp65 tm10). C) Signed posterior probabilities for a model fit per gene but across all stimulations simultaneously. D) Clustering of the signed q-values from Fisher's exact test. Genes selected from Fisher's exact test at the 10\% FDR level. This figure appears in color in the electronic version of this article.}
\label{fig:fluidigm}
\end{figure}
